---
title: ""
author: ""
params:
  week: 
  label: 
  week_number:
  year_number: 
  t: 
  full:
subparagraph: yes
geometry: margin=1.5cm
output: 
  pdf_document:
    latex_engine: xelatex
    toc: no
    number_sections: yes
    includes:
      in_header: "header.tex"
---

```{r setup, include=FALSE, error=TRUE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = TRUE, fig.width = 8, fig.height = 1.6)
library(pollster)
library(dplyr)
library(knitr)
library(ggplot2)
library(kableExtra)
library(collapse)
library(Hmisc)
library(spatstat)
library(stringr)
library(tibble)
library(forcats)
library(ggthemes)
library(dbplyr)

source("theme.r")

week <- params$week
label <-params$label
file <- params$file
week_number <- params$week_number
year_number <- params$year_number
t <- params$t
full <- params$full

# week  <- "Dec. 2-8"
# label <- "w49_2022"
# week_number <- 49
# year_number =2022
# t=""

### SQL
config_args <- config::get("dataconnection", file = '../../../../../../.secrets/config.yml')
con <- DBI::dbConnect(
    RMariaDB::MariaDB(), 
    host = config_args$server,
    user = config_args$uid,
    password = config_args$pwd,
    dbname = config_args$database,
    port = config_args$port
)

if(full=="full"){
df <- as_tibble(tbl(con, sql(paste0("select * from surveys_labelled"))) %>% collect())
}else{
df <- as_tibble(tbl(con, sql(paste0("select * from surveys_labelled where week ='", week_number, "' and year='", year_number,"'"))) %>% collect())}

df$weight <- as.numeric(df$weight)

df <- df[!is.na(df$weight),]
DBI::dbDisconnect(con)

df <- as.data.frame(df)
names(df)
 if (week =="Sept. 23-29"){
  df$engagement_measure <- df$w2_2022_1_wright_state
  df$engaged <- "Not Engaged"
  df$engaged[df$engagement_measure =="Iowa"] <- "Engaged"
  df$engaged[df$engagement_measure =="Iowa"] <- "Engaged"
} else if (week =="Sept. 20-Oct. 6"){
  df$engagement_measure <- df$w3_2022_1_wright_state
  df$engaged <- "Not Engaged"
  df$engaged[df$engagement_measure =="Iowa"] <- "Engaged"
  df$engaged[df$engagement_measure =="Iowa"] <- "Engaged"
} else {
  df$engaged <- "Not Engaged"
  df$engaged[df$engagement_measure =="Oregon"] <- "Engaged"
  
}

title <- week
if(t == "engaged"){
  df <- df %>%
    filter(engaged == "Engaged")
  
  title <- paste0(week, " - Engaged Respondents")
}

questions <- read.csv("questions.csv", stringsAsFactors=FALSE)
df$pid <- "Independent/Other"
df$pid[df$pid7 == "Strong Democrat" | df$pid7 == "Not very strong Democrat" | df$pid7 == "Lean Democrat"] <- "Democrat"
df$pid[df$pid7 == "Strong Republican" | df$pid7 == "Not very strong Republican"| df$pid7 == "Lean Republican"] <- "Republican"
df$hispanic[df$hispanic==""] <- "Skipped"

df$violence2[is.na(df$violence2) | df$violence2==""] <- "No Support"
df$violence3[is.na(df$violence3) | df$violence3==""] <- "No Support"
df$violence4[is.na(df$violence4) | df$violence4==""] <- "No Support"
df$violence5[is.na(df$violence5) | df$violence5==""] <- "No Support"
df$violence6[is.na(df$violence6) | df$violence6==""] <- "No Support"

df$age <- as.numeric(format(Sys.Date(), "%Y")) - as.numeric(df$birthyr)
df$agec[df$age <= 34] <- "18-34"
df$agec[df$age >34 & df$age <= 50 ] <- "35-50"
df$agec[df$age >50 & df$age <= 69 ] <- "51-69"
df$agec[df$age >69 ] <- "70+"

df$presvote20post[df$presvote20post == "Howie Hawkins"] <- "Other"
df$presvote20post[df$presvote20post == "Jo Jorgensen"] <- "Other"
df$presvote20post[df$presvote20post == "Did not vote for President"] <- "Didn't vote"

df$race[df$race=="Two or more races"] <- "Multiracial"

df$educ[df$educ == "High school graduate"] <- "HS Graduate"

df$bornagain <- "Not born again"
df$bornagain[df$pew_bornagain == "Yes"] <- "Born again"

MOE <- function(sample, population){
  sample = 1000
  population = .5
  d  <- 1.96 * sqrt((population * (1 - population)) / (sample))
  d = round(d*100,2)
  return(d)
}

wrapper <- function(x, ...) 
{
  paste(strwrap(x, ...), collapse = "\n")
}

section <- ""
```

```{=latex}

\includegraphics[width=.5\linewidth]{images/logo.pdf}
\vspace{2cm}
\begin{center}
  \huge{\textbf{America's Political Pulse}}\\~\\
  
  
    
```
`r title`
```{=latex}


\vspace{4cm}
 
\begin{table}[H]
\centering
\begin{tabular}{p{3.5cm}|p{7cm}}
\begin{center}
  \vspace{-1.4cm} \includegraphics[width=.75\linewidth]{images/dartmouth.png}    
\end{center}
 & \begin{tabular}[]{l}  \textbf{Sean J. Westwood}\\
Associate Professor\\ Department of Government\\ Dartmouth College\end{tabular} \\ \\



\begin{center}
    \vspace{-1cm}
     \includegraphics[width=.75\linewidth]{images/upenn.png} 
\end{center}

 & { \begin{tabular}[T]{l} \textbf{Yphtach Lelkes} \\
Associate Professor\\ Annenberg School of Communication\\ University of Pennsylvania\end{tabular}}\\ \\ \\


\begin{center}
    \vspace{-1cm}
 \includegraphics[width=.75\linewidth]{images/stanford.png}  
\end{center}

 & { \begin{tabular}[T]{l} \textbf{Shanto Iyengar} \\
William Robertson Coe Professor of American Studies\\ Department of Political Science\\ Stanford University \end{tabular}}
\end{tabular}
\end{table}
\end{center} 
\newpage
```


```{=latex}
\thispagestyle{empty}

\newpage
\setcounter{tocdepth}{4}
\tableofcontents
\newpage
```

# About

We are a cross-university research lab (Dartmouth College, University of Pennsylvania and Stanford University). The lab exists to serve as a nexus for work on affective polarization, social trust, and political violence.

Our lab focuses on addressing the following critical questions:

- What are the principal causes of affective polarization and what can be done to treat it?
- When and where does affective polarization alter behavior? Why?
- How effective and durable are approaches to reducing affective polarization?
\newpage

```{r functions, echo=FALSE, warning = FALSE, message=FALSE, results='asis'}
outcomes <- c("democrat_therm_1", "republican_therm_1", "general_trust", "institutional_corruption", "institutional_response", "vote_importance", "pride",  "fair_treatment", "norm_judges", "norm_judges_perception", "norm_polling", "norm_polling_perception", "norm_executive", "norm_executive_perception", "norm_censorship", "norm_censorship_perception", "norm_loyalty", "norm_loyalty_perception", "violence1",  "violence2",  "violence3",  "violence4",  "violence5",  "violence6") 
              
policy <- c("policy_graduated_taxes", "policy_energy_ind", "policy_labor_power", "policy_health_insur", "policy_free_trade", "policy_trans_athletes", "policy_abortion", "policy_defund_police", "policy_gun_rights", "policy_marijuana_legal", "engagement_measure")
controls <- c("pid","gender",  "race", "educ", "agec", "presvote20post", "bornagain")

df$hispanic <- recode(df$hispanic, "Yes" = "Hispanic", "No" = "Not Hispanic")

agreeDisagree <- c("Strongly agree","Agree","Neither agree nor disagree","Disagree","Strongly disagree")
supportOppose <- c("Strongly support","Support","Neither support nor oppose","Oppose","Strongly oppose")
refuseAccept <- c("Extremely likely to refuse","Likely to refuse","Equally likely to refuse or accept","Likely to accept","Extremely likely to accept")
likelyUnlikely <- c("Extremely unlikely","Unlikely","Equally likely to or unlikely","Likely","Extremely likely")
importantUnimportant <- c("Very important","Important","Neither important nor unimportant","Unimportant","Very unimportant")
proudNot <- c("Extremely proud","Very proud","Moderately proud","Only a little proud","Not at all proud")
yesNo <- c("Yes", "No")

getPlot <- function(df, outcome, type, question_text){
  # df = df
  # outcome = outcomes[23]
  # type = supportOppose
  if(str_detect(outcome, 'norm')){
    df_sub <- df[df[,outcome] !="",]
  }else{
    df_sub <- df
  }
  
  if((length(type)==5 & !str_detect(outcome, 'violence')) | (length(type)==5 & outcome =='violence1')){
    colors = c("#7ad151","#22a884","#2a788e","#414487","#440154")
  } else if(length(type) == 2){
    colors = c("#7ad151","#22a884")
  } else if(length(type) == 6 | str_detect(outcome, 'violence')){
    colors = c("#a0da39","#4ac16d","#1fa187","#277f8e","#365c8d", "#46327e")
  } else if(length(type) == 7){
    colors = c("#a0da39","#4ac16d","#1fa187","#277f8e","#365c8d", "#46327e", "#440154")
  }
      a<- eval(parse(text=paste("topline(df=df_sub, variable=", outcome, ", weight=weight)")))
  
  a$q <- "test"
  if(str_detect(outcome, 'violence') & outcome != "violence1"){
    a <- a %>% slice(match(c(type, "No Support"), Response)) 
    a$Response <- fct_relevel(a$Response, c(type,"No Support"))
  }else{
    a <- a %>% slice(match(type, Response)) 
    a$Response <- fct_relevel(a$Response, type)
  }
  
  plot <- ggplot(a, aes(fill=Response, y=Percent, x=q)) + 
    geom_bar(position="stack", stat="identity") + 
geom_text(check_overlap = TRUE,position = position_stack(vjust=.5),aes(label = paste(round(Percent,0),"%",sep="")), fontface = "bold",  size = 4, color="white")  +
    coord_flip() +
    ylim(0,101) +
    scale_fill_manual(values=colors) +
    guides(fill=guide_legend(title="",reverse = TRUE, byrow=TRUE), color="none") + 
    #ggtitle(wrapper(question_text,width=90)) +
    theme_prl()+ 
    theme(panel.grid.major = element_blank(),
          axis.text.y=element_blank(),
          plot.title = element_text(size=12),
          legend.text=element_text(size=9),          
          axis.title.y=element_blank(),
          axis.title.x=element_blank()) 
  return(plot)
}

getDemos <- function(df, outcome, controls, type){
  #getDemos(df, outcomes[i], controls, agreeDisagree)
   # df =df
   # i=13
   #  outcome = outcomes[i]
   #  controls = controls
   #  type = agreeDisagree
  # df <- df %>% 
  #   filter(!is.na(outcome) | outcome != "")
  # df[,outcome]
  list <- rep(NA, length(controls))
  for(j in 1:length(controls)){
    # j=6
    a<- eval(parse(text=paste("crosstab(df=df, y=", outcome, ", x=", controls[j], ", weight=weight)")))
    missing <- setdiff(type,names(a))
    if(length(missing) > 0){
      for(k in 1:length(missing)){
        k=1
          a[,missing[k]] <- rep(0, nrow(a))
      }
    }

    if(controls[j] == "pid"){
      o <- c("Democrat", "Independent/Other", "Republican")
      a <- a %>% slice(match(o,pid))
    } else if (controls[j] == "gender"){
      o <- c("Female", "Male")
      a <- a %>% slice(match(o,gender))
    } else if (controls[j] == "race"){
      o <- c("Asian", "Black", "Hispanic", "Middle Eastern", "Multiracial", "Native American", "Other", "White")
      a <- a %>% slice(match(o,race))
    } else if (controls[j] == "educ"){
      o <- c("No HS", "HS Graduate","Some college","2-year","4-year","Post-grad")
      a <- a %>% slice(match(o,educ))
    } else if (controls[j] == "agec"){
      o <- c("18-34", "35-50", "51-69", "70+")
      a <- a %>% slice(match(o,agec))
    } else if (controls[j] == "presvote20post"){
      o <- c("Didn't vote", "Donald Trump", "Joe Biden", "Other")
      a <- a %>% slice(match(o,presvote20post))
    } else if (controls[j] == "bornagain"){
      o <- c("Not born again", "Born again")
      a <- a %>% slice(match(o,bornagain))
    }
            type2 <- c()
    for(item in 1:length(type)){
      if(type[item] %in% names(a)){
        type2<- c(type2, type[item])
      }

    }

    a <- a %>% relocate(c(controls[j],n,type2)) %>%
    rename("Value" = controls[j])
    list[j] <- list(as.data.frame(a))
    b <-as.data.frame(a)
  }
  
  result <- do.call(rbind, list)
  result <- result %>% mutate_if(is.numeric, ~round(., 2))
  result$n <- round(result$n,0)
  b<-result %>% knitr::kable(
      format = "latex",
      position = "h!",
      align = c("l", rep("r", ncol(result)-2)),
      booktabs = TRUE,
      longtable = FALSE,
      linesep = "",
      ) %>%
  kableExtra::kable_styling(
      full_width =T,
      font_size = 7,
      latex_options = c("striped", "scale_down"),
      stripe_color = "gray!15"
    ) %>%
  row_spec(c(3,5,13,19, 23,27), hline_after=T) %>%
        pack_rows("Partisanship", 1, 3, indent=FALSE) %>%
    pack_rows("Sex", 4, 5, indent=FALSE) %>%
    pack_rows("Race", 6, 13, indent=FALSE) %>%
    pack_rows("Highest Education", 14, 19, indent=FALSE) %>%
    pack_rows("Age", 20, 23, indent=FALSE) %>%
    pack_rows("2020 Vote Choice", 24, 27, indent=FALSE) %>%
    pack_rows("Born again", 28, 29, indent=FALSE) 
  
  return(b)
}

getDemosNumeric <- function(df, outcome, controls){
   #  df =df
   # i=14
  list <- rep(NA, length(controls))

  for(j in 1:length(controls)){
    levels <- unique(df[,controls[j]])
    list_levels <- rep(NA, length(levels))
    for(k in 1:length(levels)){
      df_sub <- df[df[,controls[j]] == levels[k],] 
      a<- tibble( 
      Value = levels[k],
      n = length(df_sub[,outcomes[i]]),
      Min = min(df_sub[,outcomes[i]], na.rm=T),
      Max = max(df_sub[,outcomes[i]], na.rm=T),
      Mean = weighted.mean(df_sub[,outcomes[i]], weight=df_sub$weight, na.rm=T),
      #Median = weighted.median(df_sub[,outcomes[i]], w=df_sub$weight, na.rm=T),
      SD = sqrt(wtd.var(df_sub[,outcomes[i]], weights=df_sub$weight)),
      Skipped = sum(is.na(df_sub[,outcomes[i]])))
      list_levels[k] <- list(as.data.frame(a))
    }
    
    if(controls[j] == "pid"){
      o <- c("Democrat", "Independent/Other", "Republican")

    } else if (controls[j] == "gender"){
      o <- c("Female", "Male")

    } else if (controls[j] == "race"){
      o <- c("Asian", "Black", "Hispanic", "Middle Eastern", "Multiracial", "Native American", "Other", "White")

    } else if (controls[j] == "educ"){
      o <- c("No HS", "HS Graduate","Some college","2-year","4-year","Post-grad")

    } else if (controls[j] == "agec"){
      o <- c("18-34", "35-50", "51-69", "70+")

    } else if (controls[j] == "presvote20post"){
      o <- c("Didn't vote", "Donald Trump", "Joe Biden", "Other")

    } else if (controls[j] == "bornagain"){
      o <- c("Not born again", "Born again")

    }
    a<-do.call(rbind, list_levels)
    a <- a %>% slice(match(o,Value))
    list[j] <- list(a)
  }
  
  result <- do.call(rbind, list)
  result <- result %>% mutate_if(is.numeric, ~round(., 2))
  
  b<-result %>% knitr::kable(
      format = "latex",
      align = c("l", rep("r", ncol(result)-2)),
      booktabs = TRUE,
      longtable = FALSE,
      position = "h!",
      linesep = "",
      ) %>%
  kableExtra::kable_styling(
      full_width =T,
      font_size = 7,
      latex_options = c("striped", "repeat_header","scale_down"),
      stripe_color = "gray!15"
    ) %>%
  row_spec(c(3,5,13,19, 23,27), hline_after=T)%>%
        pack_rows("Partisanship", 1, 3) %>%
    pack_rows("Sex", 4, 5) %>%
    pack_rows("Race", 6, 13) %>%
    pack_rows("Highest Education", 14, 19) %>%
    pack_rows("Age", 20, 23) %>%
    pack_rows("2020 Vote Choice", 24, 27) %>%
    pack_rows("Born again", 28, 29, indent=FALSE) 
  
  return(b)
}

getTopLine <- function(df, outcome, type){
  #getDemos(df, outcomes[i], controls, agreeDisagree)
  #df, outcomes[i], refuseAccept
    # df =df
    # i=4
    #  outcome = outcomes[i]
   #  controls = controls
     # type = refuseAccept
    if(str_detect(outcome, 'norm')){
      df_sub <- df[df$norm_judges !="",]
    }else{
      df_sub <- df
    }
    a<- eval(parse(text=paste("topline(df=df_sub, variable=", outcome, ", weight=weight)")))
    if(str_detect(outcome, 'violence')){
      b<-a %>%
      slice(match(c(type, "No support"), Response )) %>%
      select(-`Cumulative Percent`) %>%
      select(-`Valid Percent`)
      
    }else{
      b<-a %>%
      slice(match(type, Response)) %>%
      select(-`Cumulative Percent`) %>%
      select(-`Valid Percent`)
    }
    
    b <- b %>% 
      mutate_if(is.numeric, ~round(., 2)) 
      
    b$Frequency <- round(b$Frequency,0)
    
    b <- b %>% knitr::kable(
    format = "latex",
    align = "l",
    position = "h!",
    booktabs = TRUE,
    longtable = FALSE,
    linesep = "",
    ) %>%
    kableExtra::kable_styling(
      full_width = T,
      latex_options = c("striped", "repeat_header"),
      stripe_color = "gray!15"
    ) 
    return(b)
}

getDemoTopLine <- function(df, control, type){
    df_sub <- df
    a<- eval(parse(text=paste("topline(df=df_sub, variable=", control, ", weight=weight)")))
    b<-a %>%
    slice(match(type, Response)) %>%
    select(-`Cumulative Percent`) %>%
    select(-`Valid Percent`)
    
    b <- b %>% 
      mutate_if(is.numeric, ~round(., 2)) 
      
    b$Frequency <- round(b$Frequency,0)
    
    b <- b %>% knitr::kable(
    format = "latex",
    align = "l",
    position = "h!",
    booktabs = TRUE,
    longtable = FALSE,
    linesep = "",
    ) %>%
    kableExtra::kable_styling(
      full_width = T,
      latex_options = c("striped", "repeat_header"),
      stripe_color = "gray!15"
    ) 
    return(b)
}

```


```{r processQuestions, echo=FALSE, warning = FALSE, message=FALSE, results='asis', error=TRUE}
for(i in 1:length(outcomes)){

  if("Strongly agree" %in% df[,outcomes[i]]){
    a <- getTopLine(df, outcomes[i], agreeDisagree)
    b <- getDemos(df, outcomes[i], controls, agreeDisagree)
    plot <- getPlot(df, outcomes[i], agreeDisagree, questions$question_text[i])
  } else if (sum(str_detect(df[,outcomes[i]], 'ppose'), na.rm=T) > 0 | sum(str_detect(df[,outcomes[i]], 'upport'), na.rm=T) > 0){
    a <- getTopLine(df, outcomes[i], supportOppose)
    b <- getDemos(df, outcomes[i], controls, supportOppose)
    plot <- getPlot(df, outcomes[i], supportOppose, questions$question_text[i])
  } else if ("Extremely likely to refuse" %in% df[,outcomes[i]]){
    a <- getTopLine(df, outcomes[i], refuseAccept)
    b <- getDemos(df, outcomes[i], controls, refuseAccept)
    plot <- getPlot(df, outcomes[i], refuseAccept, questions$question_text[i])
  } else if ("Extremely unlikely" %in% df[,outcomes[i]]){
    a <- getTopLine(df, outcomes[i], likelyUnlikely)
    b <- getDemos(df, outcomes[i], controls, likelyUnlikely)
    plot <- getPlot(df, outcomes[i], likelyUnlikely, questions$question_text[i])
  } else if ("Very important" %in% df[,outcomes[i]]){
    a <- getTopLine(df, outcomes[i], importantUnimportant)
    b <- getDemos(df, outcomes[i], controls, importantUnimportant)
    plot <- getPlot(df, outcomes[i], importantUnimportant, questions$question_text[i])
  } else if ("Extremely proud" %in% df[,outcomes[i]]){
    a <- getTopLine(df, outcomes[i], proudNot)
    b <- getDemos(df, outcomes[i], controls, proudNot)
    plot <- getPlot(df, outcomes[i], proudNot, questions$question_text[i])
  } else if ("Yes" %in% df[,outcomes[i]]){
    a <- getTopLine(df, outcomes[i], yesNo)
    b <- getDemos(df, outcomes[i], controls, yesNo)
    plot <- getPlot(df, outcomes[i], yesNo, questions$question_text[i])
  }else if (is.numeric(df[,outcomes[i]])){
    a<- tibble(
    n = length(df[,outcomes[i]]),
    Min = min(df[,outcomes[i]], na.rm=T),
    Max = max(df[,outcomes[i]], na.rm=T),
    Mean = weighted.mean(df[,outcomes[i]], weight=df$weight, na.rm=T),
    Median = weighted.median(df[,outcomes[i]], w=df$weight, na.rm=T),
    SD = sqrt(wtd.var(df[,outcomes[i]], weights=df$weight)),
    Skipped = sum(is.na(df[,outcomes[i]])))

    a <- a %>% 
      mutate_if(is.numeric, ~round(., 2)) 
    
    a <- a %>% knitr::kable(
    format = "latex",
    position = "h!",
    align = "l",
    booktabs = TRUE,
    longtable = FALSE,
    linesep = "",
    ) %>%
    kableExtra::kable_styling(
      full_width = T,
      latex_options = c("striped", "repeat_header"),
      stripe_color = "gray!15"
    ) 
    b <- getDemosNumeric(df, outcomes[i], controls)
  }
  
  if(section != questions$section[i]){
    cat(paste("\n# ", questions$section[i],"\n"))
    section = questions$section[i]
  }
  
  question <- questions$question_text[i]
  question <- str_replace_all(question, "\\{", "\\\\{")
  question <- str_replace_all(question, "\\}", "\\\\}")
  
  cat(paste("\\begin{flushleft} \\textbf{Question label:} ", str_replace_all(questions$label[i], "_", "\\\\_")," \\break \\break \\textbf{Question text:} \`\`",question,"\'\' \\end{flushleft}", sep=""))
  if (!is.numeric(df[,outcomes[i]])){
  print(plot)
  }
    
  cat("\\textbf{Responses}")
  print(a) # <-- this are causing errors on the main server
  cat("\n")
    cat("\\textbf{Responses by Demographics}")
  print(b) # <-- this are causing errors on the main server
  if(questions$notes[i] != ""){
      cat(paste("\\footnotesize Notes: ",questions$notes[i]))
  }

  cat("\n\\clearpage\\pagebreak\n")
}
```
\newpage

# Demographics

```{r echo=FALSE, warning = FALSE, message=FALSE, results='asis', error=TRUE}
for(j in 1:length(controls)){

  if(controls[j] == "pid"){
      o <- c("Democrat", "Independent/Other", "Republican")
      a <- getDemoTopLine(df, controls[j], o)
      label <- "Partisanship"
    } else if (controls[j] == "gender"){
      o <- c("Female", "Male")
      a <- getDemoTopLine(df, controls[j], o)
      label <- "Sex"
    } else if (controls[j] == "race"){
      o <- c("Asian", "Black", "Hispanic", "Middle Eastern", "Multiracial", "Native American", "Other", "White")
      a <- getDemoTopLine(df, controls[j], o)
      label <- "Race"
    } else if (controls[j] == "educ"){
      o <- c("No HS", "HS Graduate","Some college","2-year","4-year","Post-grad")
      a <- getDemoTopLine(df, controls[j], o)
      label <- "Highest level of education"
    } else if (controls[j] == "agec"){
      o <- c("18-34", "35-50", "51-69", "70+")
      a <- getDemoTopLine(df, controls[j], o)
      label <- "Age"
    } else if (controls[j] == "presvote20post"){
      o <- c("Didn't vote", "Donald Trump", "Joe Biden", "Other")
      a <- getDemoTopLine(df, controls[j], o)
      label <- "2020 Vote Choice"
    } else if (controls[j] == "bornagain"){
      o <- c("Not born again", "Born again")
      a <- getDemoTopLine(df, controls[j], o)
      label <- "Born again"
    }
    cat(paste("\\textbf{", label, "}"))
    cat(a) # <-- this are causing errors on the main server

}
```

\newpage

# Methods

Data were collected from a nationally representative sample of `r formatC(nrow(df), format="d", big.mark=",")` American adults via YouGov.  Data were collected between `r week` 2022. All results are weighted.  The survey margin of error is +/- `r MOE(nrow(df),209128094)`%.


